Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
added a few more minor edits to the captions

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.jpg}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.jpg}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses. In this example which was captured at thirty frames per second, the presented algorithm took 0.0158s per frame in a Python implementation.  In this figure, the dot is the start point of the test trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory.}
	\label{fig:gates-1-2}
\end{figure}

@@

	\caption{An illustration of the predictions generated by the various algorithms. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} suffer from the inability of their motion model to adequately match the speed of the agent.}

@@

	\caption{An illustration of the predictions generated by the various algorithms. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle.}

>>>>

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.jpg}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.jpg}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses.  In this figure, the dot is the start point of the test trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory. The likelihood of detection is depicted using the \textit{virdis} color palette. In this example which was captured at thirty frames per second, the presented algorithm took 0.0158s per frame in a Python implementation. }
	\label{fig:gates-1-2}
\end{figure}

@@

	\caption{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory. The likelihood of detection is depicted using the \textit{virdis} color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} suffer from the inability of their motion model to adequately match the speed of the agent.}

@@

	\caption{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory. The likelihood of detection is depicted using the \textit{virdis} color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle.}
